That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-20 ms.tex
sig test

\begin{abstract}
The planet Kepler-1625b was recently suggested to have an EXOMOON. We present here a reanalysis of the \HST/WFC3 observations of the Kepler-1625 system. We find that the data are well fit with a single transit model. We also do a moon model, and it is not favored. Upper limit on moon. Instrument systematics? Focus searches for exomoons on alternative targets.
\end{abstract}

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b, is fairly long-period large world, with a radius consistent with that of Jupiter and an orbital period of 287 days. 
long period makes it ideal for stability of moon!

It was discovered in the Analysis of the four-year \Kepler\ mission  \citep{teachey18b}.

Of the FIXME transits observed by \Kepler\, FIXME what did they show.

Recently, analysis by FIXME of \Kepler\ observations of FIXME suggested a moon. Follow-up happened.

\citep{rodenbeck18} found moon was model dependent

%Given the extraordinary nature of this claim, we wished to present a reanalysis.

@@

In brief, optimal extraction is an iterative procedure with the following steps. First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum. We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$. We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.  We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve. The data reported in this work use $\sigma_\mathrm{cut} = 15$.  To create the braodband transit light curve, we sum each spectrum over all wavelengths.

@@

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein??}. In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius $R_*$, the planet radius $R_\mathrm{planet}$, the time of central transit $t_\mathrm{planet}$, and the planet inclination $i$. For the moon model, we added a third body with radius $R_\mathrm{moon}$, transit time $t_\mathrm{moon}$, and orbital period $P_\mathrm{moon}$. We fixed the inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.  We also fixed the moon mass and eccentricity to zero.  We fixed the planet's orbital period to 287.378949 days \citep{teachey18b}. For both the moon and no-mooon models, we fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$. The \texttt{planetplanet} model uses these input parameters and returns the relative system flux for each exposure.

@@

We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend. A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}. The model is:
\begin{equation}
S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
\end{equation}
where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  For comparison, we also fit the raw light curve from \cite{teachey18b}.  In total, we fit each data set with four different models:

\begin{enumerate}
\item{No moon, non-parametric ramp, X-Y decorrelation} 
\item{Moon, non-parametric ramp, X-Y decorrelation} 
\item{No moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
\item{Moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
\end{enumerate}

For each model, we determined the best fit parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps.

@@

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
    \caption{Posterior distributions}
\label{fig:corner}
\end{figure}

@@

\acknowledgments
Alex Teachey, Dan Foreman-Mackey

The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{reinliu2012rebound}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

>>>>

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a reanalysis of the Hubble observations. We find that the transit light curve is well fit with a single orbiting body, and that the addition of a moon does not significantly improve the fit quality. The $3\,\sigma$ upper limit on the moon radius is FIXME. FIXME: why are we different from TK18?  We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
\end{abstract}

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.  The first evidence for the exomoon candidate, Kepler-1625b I, came from three transit observations from the \Kepler\ primary mission that showed FIXME \citep{teachey18a}...

%Of the FIXME transits observed by \Kepler\, FIXME what did they show.

%Recently, analysis by FIXME of \Kepler\ observations of FIXME suggested a moon. Follow-up happened.

%\citep{rodenbeck18} found moon was model dependent

@@

In brief, optimal extraction is an iterative procedure with the following steps. First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum. We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$. We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.  We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve. The data reported in this work use $\sigma_\mathrm{cut} = 15$.  To create the broadband transit light curve, we sum each spectrum over all wavelengths.

@@

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}. The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.

In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius $R_*$, the planet radius $R_\mathrm{planet}$, the time of central transit $t_\mathrm{planet}$, and the planet inclination $i$. For the moon model, we added a third body with radius $R_\mathrm{moon}$, transit time $t_\mathrm{moon}$, and orbital period $P_\mathrm{moon}$. We allowed the moon period to vary from 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.

The models also had several fixed parameters. For the moon model, we fixed inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.  We also fixed the moon mass and eccentricity to zero.  For both the no-moon and moon models, we fixed the planet's orbital period to 287.378949 days \citep{teachey18b}. We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.  These choices restrict the orbital FIXME

@@

%We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend. A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}. The model is:
%\begin{equation}
%S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
%\end{equation}
%where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  For comparison, we also fit the raw light curve from \cite{teachey18b}.  We determined the best fit model parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps. We discarded the first 20\% of the MCMC chain as burn-in. As a quick test for convergence, we divided the remainder of the chain in half and checked that the results from the first half were consistent with the second half.

%\begin{enumerate}
%\item{No moon, non-parametric ramp, X-Y decorrelation} 
%\item{Moon, non-parametric ramp, X-Y decorrelation} 
%\item{No moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
%\item{Moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
%\end{enumerate}

@@

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
    \caption{Posterior distributions for the moon radius and time of central transit. Blue = this work; red = our analysis of TK18 data.}
\label{fig:corner}
\end{figure}

@@

\acknowledgments
Dan Foreman-Mackey

The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.
